D3692R1: How to Avoid OOTA Without Really Trying

### 2025-06-13 paper/ootavacuous.tex
ootavacuous: Add presenting author's email address
(I was chided for having left this out by working-group chairs who
need to be able to get in touch with the author who will be presenting.
I am assuming that Alan Stern won't be in Sofia next week, so that would
be me.)

Signed-off-by: Paul E. McKenney <paulmck@kernel.org>
ootavacuous: Add Alan email, standard non-request, D-number paper
Signed-off-by: Paul E. McKenney <paulmck@kernel.org>

\begin{document}
\title{P3692R0: How to Avoid OOTA Without Really Trying}

@@

\author{
Alan Stern \and
Paul E.~McKenney \and
Michael Wong \and
Maged Michael
}

@@

	It follows that enforcing OOTA avoidance requires no special
	action from implementations and no changes to user code.

>>>>

\begin{document}
\title{D3692R1: How to Avoid OOTA Without Really Trying}

@@

\author{
Alan Stern (stern@rowland.harvard.edu) \and
Paul E.~McKenney (paulmckrcu@gmail.com) \and
Michael Wong \and
Maged Michael
}

@@

	It follows that enforcing OOTA avoidance requires no special
	action from implementations and no changes to user code.
	As a consequence, we are not asking for any normative changes
	to the standard.
